\texttt{MSnbase}, efficient R-based processing and visualisation of raw mass spectrometry data

### 2020-04-27 msnbase2.Rnw
fix one of many typos

The authors thank the various contributors and users who have provided
constructuve input and feedback that have helped, over the years, the
improvement of the package. The authors declare no conflict of
interest.

>>>>

The authors thank the various contributors and users who have provided
constructive input and feedback that have helped, over the years, the
improvement of the package. The authors declare no conflict of
interest.
